---
title: "Customization"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{customization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CorrGrapheR)
```

## Custom correlation coefficients

### calculate_cors function

As mentioned in introduction, calculating comparable corelation coefficients between variables of different types is a non-trivial problem. The `CorrGrapheR` package provides user with ability to experiment with different measures of correlation, using `calculate_cors` function.

The `num_num_f`, `num_cat_f` and `cat_cat_f` arguments should be functions, used to calculate correlation coefficients between different pairs variables, respectively. Each of them should take 2 arguments (vectors of equal length; for `num_num_f` - both `numeric`, for `cat_cat_f` - both `factor`, for `num_cat_f` - **first** `numeric` and **second** `factor`) and return a single number. It should be intepretable in the following way: the bigger its absolute value, the stronger correlation between variables. If it's negative - the variables are negatively correlated.

When supplying custom functions, a `max_cor` argument is required. It should be a single number indicating strongest possible correlation (like 1 in Pearson's `cor.test`). It is used when calculating correlation between the same variables, to trim accidental results above it and to scale final results into $[-1,1]$ range.

The `calculate_cors` returns a correlation `matrix`, similarly to `cor`.

```{r cors}
df <- as.data.frame(datasets::Seatbelts)[,1:5]
f1 <- function(x, y) cor.test(x, y, method = 'pearson')$estimate
f2 <- function(x, y) cor.test(x, y, method = 'kendall')$estimate
f3 <- function(x, y) cor.test(x, y, method = 'spearman', exact = FALSE)$estimate
calculate_cors(df, num_num_f = f1, max_cor = 1)
calculate_cors(df, num_num_f = f2, max_cor = 1)
calculate_cors(df, num_num_f = f3, max_cor = 1)
```

As we see, user has to supply only necessary functions for given `x` argument. For a `data.frame` only with `numeric` data only `num_num_f` is required. 

Since correlation meaures for different data variables are **not** comparable in most cases, it requried from the user to **always** supply **all** necessary functions. Naturally, user might supply function identical to the default:

```{r cors_mixed}
data(dragons, package = 'DALEX')
f1 <- function(x, y) -log10(cor.test(x, y, method = 'spearman', exact = FALSE)$p.value)
f2 <- function(x, y) -log10(kruskal.test(x, y)$p.value)
calculate_cors(dragons, 
               num_num_f = f1, 
               num_cat_f = f2,
               max_cor = 100)
```

### Inside corrgrapher function

`calculate_cors` is called inside `corrgrapher` function. User may pass custom functions to it via `cor_functions` argument. It should be a named `list` with `num_num_f`, `num_cat_f`, `cat_cat_f` and `max_cor` elements.

```{r cors_passed}
corrgrapher(df,
            cor_functions = list(num_num_f = f1, 
                                 num_cat_f = f2, 
                                 max_cor = 100))
```

## Custom feature importance

When `corrgrapher` function is called on an `explainer` object, it calculates inside importance of features (variables) using `ingredients::feature_importance` function. User may (sometimes should) supply `feature_importance` argument as either:

 * An object created using `ingredients::feature_importance` on **the same** `explainer`, or
 * A named list of parameters to pass to `ingredients::feature_importance` called inside `corrgrapher` function.
 
Remember, do **not** change `variables` and `variable_groups` arguments.
 
```{r feat, cache=TRUE}
library(ranger)
library(DALEX)
data("titanic_imputed", package='DALEX')
tit_model <- ranger(survived ~ ., data = titanic_imputed, num.trees = 100)
tit_model_exp <- explain(tit_model,
                         data = titanic_imputed[,-8],
                         y = titanic_imputed[, 8],
                         verbose = FALSE)
tit_model_fi <- ingredients::feature_importance(tit_model_exp,
                                                B = 5,
                                                loss_function = loss_accuracy)
tit_cgr_1 <- corrgrapher(tit_model_exp, feature_importance = tit_model_fi)
tit_cgr_2 <- corrgrapher(tit_model_exp, 
                         feature_importance = list(B = 20,
                                                   loss_function = loss_one_minus_auc))
tit_cgr_1
tit_cgr_2
```

## Custom partial dependence

Similarly to `feature_importance`, user may (sometimes should) supply `partial_dependency` argument. Do **not** change `variable_type`, `variables` or `variable_splits` arguments.

```{r pds, cache=TRUE}
tit_model_pds <- ingredients::partial_dependence(tit_model_exp, grid_points = 50, N = 100)

tit_cgr_3 <- corrgrapher(tit_model_exp, 
                         feature_importance = tit_model_fi,
                         partial_dependency = tit_model_pds)
tit_cgr_4 <- corrgrapher(tit_model_exp, 
                         feature_importance = tit_model_fi,
                         partial_dependency = list(grid_points = 101,
                                                   N = 200))

tit_cgr_3
tit_cgr_4
```