---
title: "Vignette"
author: "Paweł Morgen"
  
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE)
data('fifa_cgr', package = 'CorrGrapheR')
data('dragons_cgr', package = 'CorrGrapheR')
```

## CorrGrapheR

This package aims to plot correlations between variables in form of a graph. Variables correlated with each other shall be close (posivitely and negatively alike), and weakly correlated  - far from each other.

It is achieved through a physical simulation, where the nodes are treated as points with mass (and are pushing each other away) and edges are treated as mass-less springs. The length of a spring depends on absolute value of correlation between connected nodes. The bigger the correlation, the shorter the spring.

## Example 1 - Seatbelts

```{r cars, message=FALSE}
library('CorrGrapheR')
library('magrittr')
df <- as.data.frame(datasets::Seatbelts)[,-8] # Drop the binary variable
corrgrapher(df) %>%
  plot()
```

```{r titanic, eval=FALSE, include=FALSE}
library("randomForest")

titanic <- na.omit(titanic)
model_titanic_rf <- randomForest(survived == "yes" ~ .,
                                 data = titanic)
explain_titanic_rf <- DALEX::explain(model_titanic_rf,
                              data = titanic[,-9],
                              y = titanic$survived == "yes",
                              label = "Random Forest")
feature_importance_titanic_rf <- ingredients::feature_importance(explain_titanic_rf)

corrgrapher(explain_titanic_rf, feature_importance = feature_importance_titanic_rf) %>% 
  plot()
```

## Example 2 - FIFA

```{r fifa_show, eval=FALSE}
library("gbm")

data('fifa20', package = 'CorrGrapheR')
fifa20_selected <- fifa20[,c(4,5,7,8,11:13,17,25:26,45:78)]

# Value is skewed. Will be much easier to model sqrt(Value).

fifa20_selected$value_eur <- log10(fifa20_selected$value_eur)
fifa20_selected$team_position <- factor(fifa20_selected$team_position)
fifa20_selected <- na.omit(fifa20_selected)
fifa20_selected <- fifa20_selected[fifa20_selected$value_eur > 0,]
fifa20_selected <- fifa20_selected[!duplicated(fifa20_selected[,1]),]
rownames(fifa20_selected) <- fifa20_selected[,1]
fifa20_selected <- fifa20_selected[,-1]

# create a gbm model

set.seed(1313)

# 4:5 are overall and potential, too strong predictors
fifa_gbm <- gbm(value_eur ~ . , data = fifa20_selected[,-(4:5)], n.trees = 250, interaction.depth = 3)

# Create DALEX explainer

fifa_gbm_exp <- DALEX::explain(fifa_gbm, 
                        data = fifa20_selected[, -6], 
                        y = 10^fifa20_selected$value_eur, 
                        predict_function = function(m,x) 
                          10^predict(m, x, n.trees = 250))

# Create table with feature importance info - not necessary

fifa_feat <- ingredients::feature_importance(fifa_gbm_exp)
fifa_pd <- ingredients::partial_dependency(fifa_gbm_exp)
# Finally, create a corrgrapher object
fifa_cgr <- corrgrapher(fifa_gbm_exp, cutoff = 0.4, 
                        feature_importance = fifa_feat,
                        partial_dependency = fifa_pd)
```

Thanks to implementation of `knit_print()` method, an object of class `corrgrapher` can be displayed simply by calling it:

```{r fifa_plot}
fifa_cgr
```

## Example 3 - dragons dataset

```{r dragons_setup, eval=FALSE}
library(ranger)
data(dragons, package='DALEX')
model <- ranger::ranger(colour ~ ., data = dragons, num.trees = 100, probability = TRUE)
model_exp <- DALEX::explain(model, data = dragons[,-5], y = dragons$colour)
model_fi <- ingredients::feature_importance(model_exp, 
                                            loss_function = DALEX::loss_accuracy, 
                                            type = 'raw')
model_pd <- ingredients::partial_dependence(model_exp, N=100, grid_points = 81)

dragons_cgr <- corrgrapher(model_exp, 
                       feature_importance = model_fi,
                       partial_dependency = model_pd)
```

```{r dragons_plot}
dragons_cgr
```

## HTML Report

If you wish to save info about single `corrgrapher` object, use `save_cgr_to_html()` function:

```{r html, eval=FALSE}
## NOT RUN
save_cgr_to_html(fifa_cgr)
```