---
title: "Vignette"
author: "Paweł Morgen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(CorrGrapheR)
library(dplyr)
```

## CorrGrapheR

This package aims to plot correlations between variables in form of a graph. Variables correlated with each other shall be close (posivitely and negatively alike), and weakly correlated  - far from each other.

It is achieved through a physical simulation, where the nodes are treated as points with mass (and are pushing each other away) and edges are treated as mass-less springs. The length of a spring depends on absolute value of correlation between connected nodes. The bigger the correlation, the shorter the spring.

## Example 1 - Seatbelts

```{r cars}
df <- as.data.frame(datasets::Seatbelts) %>%
  select(-law)
plot_corrgraph(df)
```

## Example 2 - FIFA

```{r fifa}
load(normalizePath('../data/fifa20.rda'))
fifa20_selected <- fifa20[,c(4,5,7,8,11:13,17,25:26,45:78)]
plot_corrgraph(fifa20_selected, cutoff = 0.3)
```

